Experiment

### 2018-06-25 experiment.Rmd
Move actual experiment to external file for reuse

## Consent

***Q1.1***: You have been invited to participate in an academic research survey about international nongovernmental organizations. This study is being conducted by Suparna Chaudhry from Christopher Newport University and Andrew Heiss from Brigham Young University. The experiment should take about **5 minutes** to complete. You will be paid **$0.75** for your participation.

Your participation in this study is entirely voluntary and you are free to skip any question or withdraw from the experiment at any time. You will not be asked to provide any personal information, and your answers will remain anonymous. There are no reasonably foreseeable risks or discomforts associated with participating in this study. There will be questions designed to check that you’re paying attention to the details of the experiment. If you answer these incorrectly, the survey will end early and you may not receive compensation.

Beyond your payment, you will receive no direct benefits from participating in this research study, but your responses may reveal important and useful insights about international NGOs and philanthropy.

If you have any questions at any time about the study or the procedures, you can contact Suparna Chaudhry (suparna.chaudhry@cnu.edu; Reiff Center for Human Rights and Conflict Resolution, Christopher Newport University, Newport News, VA 23606) or Andrew Heiss (andrew_heiss@byu.edu; Romney Institute of Public Management, Brigham Young University, Provo, UT 84602) at andrew_heiss@byu.edu. This research has been reviewed by the Institutional Review Board at Christopher Newport University (757-594-7461; IRB@cnu.edu) and the IRB administrator at Brigham Young University (801-422-1461; irb@byu.edu).

By clicking "I agree" below you are indicating that you are at least 18 years old, have read and understood this consent form and agree to participate in this research study. Please print a copy of this page for your records.

*Q1.2*: I have read the above information, and I consent to take part in the study.

:   Single answer

    - Yes
    - No

---

*Q1.3*: Please read the paragraph below carefully.

What is your favorite color? While we are interested in learning about your preferences on a variety of topics, including colors, we also want to make sure that you are reading the questions we have written. To demonstrate that you’ve read this much, just go ahead and select both green and yellow from among the alternatives listed below, no matter what your favorite color is. Yes, ignore the first sentence and select both green and yellow.

**(End survey without payment if this question is incorrect.)**

: Multiple answers allowed (*must be green and yellow*)

    - Pink
    - Red
    - Green
    - White
    - Yellow
    - Blue

---

## Crackdown and private giving

*Q2.1*: How do you feel about the following types of organizations?

:   Matrix table

    |                                                                          | Very unfavorable | Unfavorable | Neutral | Favorable | Very favorable |
    |--------------------------------------------------------------------------|:----------------:|:-----------:|:-------:|:---------:|:--------------:|
    | Nonprofit organizations that provide humanitarian relief                 |         ⊚        |      ⊚      |    ⊚    |     ⊚     |        ⊚       |
    | Nonprofit organizations that advocate for human rights                   |         ⊚        |      ⊚      |    ⊚    |     ⊚     |        ⊚       |
    | Nonprofit organizations that help with development and alleviate poverty |         ⊚        |      ⊚      |    ⊚    |     ⊚     |        ⊚       |

---

![](img/irc_logo.png "IRC logo"){.img-responsive .center}

\

*Q2.2*: The **International Rescue Committee** (IRC) focuses on {ISSUE AREA: humanitarian assistance for refugees | human rights for refugees} {MAIN MANIPULATION: and works in countries that have recently passed laws that harshly restrict nonprofit organizations}.

A substantial proportion of IRC’s funding comes from {FUNDING SOURCE: government | private donors}.

*Q2.3*: How likely would you be to donate to IRC?

:   Single answer

    - Extremely likely
    - Somewhat likely
    - Neither likely nor unlikely
    - Somewhat unlikely
    - Extremely unlikely

*Q2.4*: If you had an extra $100, how much would you be willing to donate to IRC right now? (*Total must add to 100*)

:   Numeric slider, options must sum to 100

    - Donate to IRC (0–100)
    - Keep for yourself (0–100)

*Q2.5*: Why did you select that amount?

:   Text field

---

## Demographics

*Q3.1*: Almost done! This is the last page of the study.

*Q3.2*: How often do you donate to charity (either cash or in-kind)?

:   Single answer

    - Once a week
    - Once a month
    - Once every three months
    - Once every six months
    - Once a year
    - Once every few years
    - Never

*Q3.3*: Have you volunteered in the past 12 months?

:   Single answer

    - Yes
    - No

*Q3.4*: Some people seem to follow what's going on in government and public affairs most of the time, whether there's an election going on or not. Others aren't that interested. Would you say that you follow what's going on in government and public affairs…

:   Single answer

    - Most of the time
    - Some of the time
    - Only now and then
    - Hardly at all

*Q3.5*: How would you describe your political views?

:   Single answer

    - Strong liberal
    - Liberal
    - Independent, leaning liberal
    - Independent
    - Independent, leaning conservative
    - Conservative
    - Very conservative

*Q3.6*: What is the highest degree or level of school you have completed?

:   Single answer

    - Less than high school
    - High school graduate
    - Some college
    - 2 year degree
    - 4 year degree
    - Graduate or professional degree
    - Doctorate

*Q3.7*: Aside from weddings and funerals, how often do you attend religious services?

:   Single answer

    - More than once a week
    - Once a week
    - Once or twice a month
    - A few times a year
    - Seldom
    - Never
    - Don't know

*Q3.8*: Please select blue from the following list:

:   Single answer

    - Red
    - Yellow
    - Blue
    - Green

*Q3.9*: What is your gender?

:   Single answer

    - Female
    - Male
    - Transgender
    - Other:
    - Prefer not to say

*Q3.10*: What is your total household income?

:   Single answer

    - Less than $10,000
    - $10,000 - $19,999
    - $20,000 - $29,999
    - $30,000 - $39,999
    - $40,000 - $49,999
    - $50,000 - $59,999
    - $60,000 - $69,999
    - $70,000 - $79,999
    - $80,000 - $89,999
    - $90,000 - $99,999
    - $100,000 - $149,999
    - More than $150,000

*Q3.11*: How old are you?

:   Single answer

    - Under 18
    - 18 - 24
    - 25 - 34
    - 35 - 44
    - 45 - 54
    - 55 - 64
    - 65 - 74
    - 75 - 84
    - 85 or older

>>>>

```{r child = "text/experiment.md"}
```
